Kelompok 4_Praktikum_Pekan 8

### 2024-04-08 Project/Kelompok 4_Praktikum_Pekan 8.Rmd
Update

```{r fig.height=6.5, fig.width=15, dpi=300}
set.seed(361)
norm_data <- rnorm(1000, mean = 0, sd = 1)
hist(norm_data, main = "Histogram Normal", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#4664AF")
```

@@

```{r fig.height=6.5, fig.width=15, dpi=300}
set.seed(361)
csq_data <- rchisq(1000, df = 1)
mixed_data_1 <- c(norm_data[1:500], csq_data[1:500])
hist(mixed_data_1, main = "Histogram Campuran 1", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#9F4274")
```

>>>>

```{r fig.height=6.5, fig.width=30, dpi=300}
set.seed(361)
k <- 1000
sample_sizes <- c(4, 12, 20, 60, 100)

norm_data <- lapply(sample_sizes, function(n) matrix(rnorm(n*k, mean = 0, sd = 1),k))

par(mfrow = c(1, 5))
hist(norm_data[[1]], main = "Sebaran Normal\nUkuran sample (n=4)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#4664AF")
hist(norm_data[[2]], main = "Sebaran Normal\nUkuran sample (n=12)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#4664AF")
hist(norm_data[[3]], main = "Sebaran Normal\nUkuran sample (n=20)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#4664AF")
hist(norm_data[[4]], main = "Sebaran Normal\nUkuran sample (n=60)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#4664AF")
hist(norm_data[[5]], main = "Sebaran Normal\nUkuran sample (n=100)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#4664AF")
```

@@

```{r}
set.seed(361)
k <- 1000
sample_sizes <- c(4, 12, 20, 60, 100)

csq_data <- lapply(sample_sizes, function(n) matrix(rchisq(n*k, df = 1), k))

mixed_data_1 <- c(norm_data[1:500], csq_data[1:500])

par(mfrow = c(1, 5))
hist(norm_data[[1]], main = "Sebaran Normal\nUkuran sample (n=4)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#4664AF")
hist(norm_data[[2]], main = "Sebaran Normal\nUkuran sample (n=12)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#4664AF")
hist(norm_data[[3]], main = "Sebaran Normal\nUkuran sample (n=20)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#4664AF")
hist(norm_data[[4]], main = "Sebaran Normal\nUkuran sample (n=60)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#4664AF")
hist(norm_data[[5]], main = "Sebaran Normal\nUkuran sample (n=100)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#4664AF")
```

```{r fig.height=6.5, fig.width=15, dpi=300}
set.seed(361)

csq_data <- rchisq(1000, df = 1)

mixed_data_1 <- c(norm_data[1:500], csq_data[1:500])

hist(mixed_data_1, main = "Histogram Campuran 1", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#9F4274")
```
